Clustering of Last.fm Music

### 2015-05-07 writeup/MSDgroupwriteup.tex
Update MSDgroupwriteup.tex

We used two different baseline benchmarks to compare our MAP scores against. THe first was to simply recommend the top 500 most popular songs to every user. This naive method resulted in a MAP score of 0.013 (top 500 songs based on number of users who listened to the song) or 0.012 (top 500 songs based on number of plays the song had). The second method was to first recommend a user the most popular songs of artists the user already had played (but different songs from that artist). If this did not result in enough recommendations, we would then recommend the overall most popular songs as well at the end(similar to baseline method 1). Although this method is conservative in that it does not go beyond the tastes the user has already listened to, it resulted in a significant improvement in the MAP score to 0.045.

>>>>

We used two different baseline benchmarks to compare our MAP scores against. THe first was to simply recommend the top 500 most popular songs to every user. This naive method resulted in a MAP score of 0.0138 (top 500 songs based on number of users who listened to the song) or 0.0126 (top 500 songs based on number of plays the song had). The second method was to first recommend a user the most popular songs of artists the user already had played (but different songs from that artist). If this did not result in enough recommendations, we would then recommend the overall most popular songs as well at the end(similar to baseline method 1). Although this method is conservative in that it does not go beyond the tastes the user has already listened to, it resulted in a significant improvement in the MAP score to 0.045.
